---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/",
  global.par = TRUE
)
library(utsOperators)
options(width=100)
```

### Introduction

This package provides rolling time series operators for unevenly spaced data, such as simple moving averages (SMAs), exponential moving averages (EMAs), and arbitrary rolling R functions. It is a wrapper around a highly-optimized [C library](http://www.eckner.com/research.html) that I released in 2012. The time series class used by this package is the [uts](https://github.com/andreas50/uts) class.

The package [rcpputs](https://github.com/eddelbuettel/rcpputs) is a low-level wrapper around the same [C library](http://www.eckner.com/research.html) that does not rely on any time series class, but instead requires the user to pass in a vector of observation values and observation times to each function.

### Installation

This package is not yet available on CRAN, but can be installled from GitHub:

```{r, eval=FALSE}
devtools::install_github(c("andreas50/uts", "andreas50/utsOperators"))  # using package 'devtools'
remotes::install_github(c("andreas50/uts", "andreas50/utsOperators"))   # ... or using package 'remotes'
```

### Sample Code

```{r}
# Get sample unevenly-spaced time series with six observations
x <- ex_uts()
x
```

```{r, eval=FALSE}
# SMA with last-point interpolation, 1-day wide rolling time window
sma(x, ddays(1))

# EMA with linear interpolation, 12-hour effective temporal length
ema(x, dhours(12), interpolation="linear")

# Rolling mean, sum, number of observation values in a 1-day wide rolling time window
rolling_apply(ex_uts(), width=ddays(1), FUN=mean)
rolling_apply(ex_uts(), width=ddays(1), FUN=sum)
rolling_apply(ex_uts(), width=ddays(1), FUN=length)
```
